Nested sampling with two objective functions

### 2015-12-14 Paper/ms.tex
update algorithm

\begin{algorithm}[ht!]
\begin{algorithmic}
\State Generate $N$ particles $\{\xx_1, ..., \xx_N\}$ from $\pi(\xx)$.
$N$ should be odd and quite large (1001 or greater).
\State Initialise the {\em remaining prior mass} to be $M=1$.
\State Initialise the {\em excluded region} $\mathcal{R}$ to be the empty set
$\emptyset$.
\While{more iterations desired}
	\State Calculate $\hat{X}(\ell_1, \ell_2)$ at the position of each particle
			and sort the $\hat{X}$ values observed.
	\State Find the median $\hat{X}$ value, $\hat{X}_{(k)}$, where $k = (N-1)/2$.
	\While{$k > 1$ and $\hat{X}_{(k-1)} = \hat{X}_{(k)}$}
		\State Set $k \leftarrow (k-1)$.
	\EndWhile
	\State Save all particles with $\hat{X} \geq \hat{X}_{(k)}$ to disk,
			assigning each a prior weight of $M/N$.
	\State Exclude the region in the $L_1$-$L_2$ plane where
$\hat{X} \geq \hat{X}_{(k)}$. That is, set
	\State \hspace{20pt} $\mathcal{R} \leftarrow \mathcal{R} \cup \{(\ell_1, \ell_2) \in \mathbb{R}^2: \hat{X}(\ell_1, \ell_2) \geq \hat{X}_{(k)}\}$.
	\State Update the remaining prior mass to $M \leftarrow M(1 - k/N)$.
	\State Replace all particles with $\hat{X} \geq \hat{X}_{(k)}$ by new
			particles generated from $\pi(\xx)$, subject to the constraint
			of not being in the excluded region.
\EndWhile
\end{algorithmic}
\caption{\label{alg:algorithm}}
\end{algorithm}

>>>>

\begin{algorithm}[ht!]
\begin{algorithmic}
\State Generate $N$ particles $\{\xx_1, ..., \xx_N\}$ from $\pi(\xx)$.
$N$ should be odd and quite large (1001 or greater).
\State Initialise the {\em remaining prior mass} to be $M=1$.
\State Initialise the {\em excluded region} $\mathcal{R}$ to be the empty set
$\emptyset$.
\While{more iterations desired}
	\State Calculate $\hat{X}(\ell_1, \ell_2)$ at the position of each particle
			and sort the $\hat{X}$ values observed.
	\State Find the median $\hat{X}$ value, $\hat{X}_{(k)}$, where $k = (N-1)/2$.
	\State Classify all particles as either ``interior'', ``boundary'', or
			``exterior'', based on whether their $\hat{X}$ values are
			greater than, equal to, or less than $\hat{X}_{(k)}$ respectively.
	\State Save all ``interior'' particles to disk, assigning each a prior weight 				of $n_{\rm interior}/(n_{\rm interior} + n_{\rm exterior})$.
	\State Exclude the region in the $L_1$-$L_2$ plane where
$\hat{X} \geq \hat{X}_{(k)}$. That is, set
	\State \hspace{20pt} $\mathcal{R} \leftarrow \mathcal{R} \cup \{(\ell_1, \ell_2) \in \mathbb{R}^2: \hat{X}(\ell_1, \ell_2) \geq \hat{X}_{(k)}\}$.
	\State Update the remaining prior mass to $M \leftarrow M n_{\rm exterior}/N$.
	\State Replace all interior and boundary particles by new
			particles generated from $\pi(\xx)$, subject to the constraint
			of not being in the excluded region.
\EndWhile
\end{algorithmic}
\caption{\label{alg:algorithm}}
\end{algorithm}
